---
title: "EL_XC_res"
author: "Jason_Wray"
date: "2025-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(patchwork)
library(plotly)
library(hms)
library(pals)
library(DT)
library(tidyverse)
```

```{r, include=FALSE, warning=FALSE}
load(file="results/processed/results.RData")
```

```{r, include=FALSE}

club_colours <- read_csv("club_info/club_colours.csv")
club_colours$club[34] <- "Hockley Trail Runners"

col_palette <- list(
  Cat = setNames(pals::warmcool(n = length(levels(res$MenHainault$Cat))), levels(res$MenHainault$Cat)), 
  club_colour = setNames(club_colours$colour, club_colours$club),
  club_fill = setNames(club_colours$fill, club_colours$club)
)

breaks <- seq(as.numeric(as_hms("00:25:00")),
             as.numeric(as_hms("01:05:00")),
             300)

```

# Essex League Cross Country 2025-2026

[Essex XC League](https://essexxcleague.org/)

# Table of Contents
1. [Overview of results for each event]
2. [Senior Men, Team Results]
3. [Veteran Men, Team Results]


## Overview of results for each event

### Table of One Tree Hill results


```{r, echo=FALSE}
datatable(res_sm$MenOneTreeHill %>%
            select(Position = Pos, 
                   Name,
                   Cat, 
                   Club, 
                   Time, 
                   Division = sm_division, 
                   `Team Position` = Team_Pos,
                   `Team Scorer` = Team_Scorer
                   ), 
          rownames = FALSE, filter = "top"
          )
```


### Table of Hainault results


```{r, echo=FALSE}
datatable(res_sm$MenHainault %>%
            select(Position = Pos, 
                   Name,
                   Cat, 
                   Club, 
                   Time, 
                   Division = sm_division, 
                   `Team Position` = Team_Pos,
                   `Team Scorer` = Team_Scorer
                   ), 
          rownames = FALSE, filter = "top")
```


### Results by category

```{r, echo=FALSE, warning=FALSE}
p <- list()

for(race in names(res)){
  
  p[[race]] <- res[[race]] %>%
    ggplot(aes(Cat, Time))+
    geom_boxplot()+
    geom_jitter(aes(colour = Club, fill=Club, 
                   text=paste0(Name, 
                               ", Club: ", Club,
                               ", Cat: ", Cat,
                             ", position: ", Pos,
                             ", Time: ", Time)))+
    scale_colour_manual(values = col_palette$club_colour)+
    scale_fill_manual(values = col_palette$club_fill)+
    scale_y_reverse(labels = function(x) as_hms(x),
                    breaks=breaks)+
    labs(x = "Category", y="Time", title = gsub("Men", "", race))+
    theme_classic()+
    theme(legend.position = "none",
          panel.background = element_rect(fill = 'slategrey'))
  
}
```

#### One Tree Hill

```{r, echo=FALSE, warning=FALSE}
ggplotly(p$MenOneTreeHill, tooltip = "text")
```

#### Hainault

```{r, echo=FALSE, warning=FALSE}
ggplotly(p$MenHainault, tooltip = "text")
```


### Results, individuals

```{r, echo=FALSE, warning=FALSE}
p <- list()

for(race in names(res)){
  
  p[[race]] <- res[[race]] %>%
    ggplot(aes(Pos, Time))+
    geom_point(aes(colour = Club, fill=Club, 
                   text=paste0(Name, 
                               ", Club: ", Club,
                               ", Cat: ", Cat,
                             ", position: ", Pos,
                             ", Time: ", Time)))+
    scale_colour_manual(values = col_palette$club_colour)+
    scale_fill_manual(values = col_palette$club_fill)+
    scale_y_reverse(labels = function(x) as_hms(x),
                    breaks=breaks)+
    labs(x = "Position", y="Time", title = gsub("Men", "", race))+
    theme_classic()+
    theme(legend.position = "none",
          panel.background = element_rect(fill = 'slategrey'))
  }
```

#### One Tree Hill

```{r, echo=FALSE, warning=FALSE}
ggplotly(p$MenOneTreeHill, tooltip = "text")
```

#### Hainault

```{r, echo=FALSE, warning=FALSE}
ggplotly(p$MenHainault, tooltip = "text")

```


### Results by club

Clubs are ordered by their team position for senior men. First 6 to score for divisions 1 and 2, 4 for division 3.

```{r, echo=FALSE, warning=FALSE}
p <- list()

for(race in names(res_sm)){
  
  p[[race]] <- res_sm[[race]] %>%
    ggplot(aes(Club, Time, colour = Club, fill=Club))+
    geom_boxplot()+
    geom_point(aes(text=paste0(Name, 
                               ", Club: ", Club,
                               ", Cat: ", Cat,
                             ", position: ", Pos,
                             ", Time: ", Time)))+
    scale_colour_manual(values = col_palette$club_colour)+
    scale_fill_manual(values = col_palette$club_fill)+
    scale_y_reverse(labels = function(x) as_hms(x),
                    breaks=breaks)+
    facet_grid(.~sm_division, scales="free_x", space="free")+
    labs(x = "", y="Time", title = gsub("Men", "", race))+
    theme_classic()+
    theme(legend.position = "none",
          axis.text.x = element_text(angle=45, hjust=1),
          panel.background = element_rect(fill = 'slategrey'))
  }
```

#### One Tree Hill

```{r, echo=FALSE, warning=FALSE}
ggplotly(p$MenOneTreeHill, tooltip = "text")
```

#### Hainault

```{r, echo=FALSE, warning=FALSE}
ggplotly(p$MenHainault, tooltip = "text")
```

## Senior Men, Team Results

```{r, echo=FALSE, warning=FALSE}
# Create list of plots 
p <- list()

for(race in names(sm_team_res)){

  p1 <- 
  ggplot(sm_team_res[[race]], 
         aes(Club, score, 
             text = paste0(Club, ", team position: ", Team_Pos, 
                           ", Team score: ", score, 
                           ", # runners: ", n_runners, 
                           ", Scorers: ", scorers)))+
  geom_point(aes(colour = Club, fill = Club), shape=21, size=3)+
  scale_colour_manual(values = col_palette$club_colour)+
  scale_fill_manual(values = col_palette$club_fill)+
  scale_y_reverse()+
  facet_grid(.~sm_division, scales="free_x")+
  labs(x = "", y="Team score", title = paste0(gsub("Men", "", race), ", Senior Men"), subtitle = "By division")+
  theme_classic()+
  theme(axis.text.x = element_blank(), 
        legend.position = "none",
        panel.background = element_rect(fill = 'slategrey'))

p2 <- 
  ggplot(res_sm[[race]], 
             aes(Club, Pos, 
                 text=paste0(Name, ", Cat: ", Cat,
                             ", position: ", Pos,
                             ", Time: ", Time)))+
  geom_point(aes(colour = Club, fill = Club, alpha = Scorer_alpha), shape=21, size=2)+
  scale_colour_manual(values = col_palette$club_colour)+
  scale_fill_manual(values = col_palette$club_fill)+
  scale_y_reverse()+
  facet_grid(.~sm_division, scales="free_x")+
  labs(x = "", y="Individual positions")+
  theme_classic()+
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position = "none",
        panel.background = element_rect(fill = 'slategrey'), strip.text=element_blank())

# Convert ggplot objects to plotly objects using ggplotly()
fig1 <- ggplotly(p1, tooltip = "text")
fig2 <- ggplotly(p2, tooltip = "text")

p[[race]] <- subplot(fig1, fig2, nrows = 2, titleY = TRUE, heights = c(0.4, 0.6))
}
```

### One Tree Hill

#### Table of Results


```{r, echo=FALSE}
datatable(sm_team_res$MenOneTreeHill %>%
            select(Division = sm_division,
                   `Team Position` = Team_Pos,
                   Club,
                   `Team Score` = score,
                   `Full Team` = Full_Team
                   ),
          rownames = FALSE, filter = "top")
```

#### Plot of Results

Clubs are ordered by their team position for senior men. First 6 to score for divisions 1 and 2, 4 for division 3.

Total team score is shown in the top row, individual scores below with scorers highlighted.


```{r, echo=FALSE, warning=FALSE, fig.dim = c(8, 8)}
p$MenOneTreeHill
```

### Hainault

#### Table of Results


```{r, echo=FALSE}
datatable(sm_team_res$MenHainault %>%
            select(Division = sm_division,
                   `Team Position` = Team_Pos,
                   Club,
                   `Team Score` = score,
                   `Full Team` = Full_Team
                   ),
          rownames = FALSE, filter = "top")
```

#### Plot of results

Clubs are ordered by their team position for senior men. First 6 to score for divisions 1 and 2, 4 for division 3.

Total team score is shown in the top row, individual scores below with scorers highlighted.


```{r, echo=FALSE, warning=FALSE, fig.dim = c(8, 8)}
p$MenHainault
```

## Veteran Men, Team Results

```{r, echo=FALSE, warning=FALSE, fig.dim = c(8, 8)}
p <- list()
for(race in names(vet_team_res)){
  
p1 <- 
  ggplot(vet_team_res[[race]], 
         aes(Club, score, text = paste0(Club, ", Team position: ", Team_Pos, ", Team score: ", score)))+
  geom_point(aes(colour = Club, fill = Club), shape=21, size=3)+
  scale_colour_manual(values = col_palette$club_colour)+
  scale_fill_manual(values = col_palette$club_fill)+
  scale_y_reverse()+
  facet_grid(.~Full_Team, scales="free_x", space="free")+
  labs(x = "", y = "Team score", title = paste0(gsub("Men", "", race), ", Vets"))+
  theme_classic()+
  theme(axis.text.x = element_blank(), 
        legend.position = "none",
        panel.background = element_rect(fill = 'slategrey'))

p2 <- 
  ggplot(res_vet[[race]], 
             aes(Club, Pos, text=paste0(Name, ", Cat: ", Cat,
                             ", Time: ", Time,
                             ", Position: ", Pos, 
                             ", Vet position: ", Vet_Pos)))+
  geom_point(aes(colour = Club, fill = Club, alpha = Scorer_alpha), shape=21, size=2)+
  scale_colour_manual(values = col_palette$club_colour)+
  scale_fill_manual(values = col_palette$club_fill)+
  scale_y_reverse()+
  facet_grid(.~Full_Team, scales="free_x", space="free")+
  labs(x = "", y="Overall position")+
  theme_classic()+
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position = "none",
        panel.background = element_rect(fill = 'slategrey'), 
        strip.text = element_blank())

# Convert ggplot objects to plotly objects using ggplotly()
fig1 <- ggplotly(p1, tooltip = "text")
fig2 <- ggplotly(p2, tooltip = "text")

p[[race]] <- subplot(fig1, fig2, nrows = 2, titleY = TRUE, heights = c(0.4, 0.6))
}
```

### One Tree Hill

#### Table of Results


```{r, echo=FALSE}
datatable(vet_team_res$MenOneTreeHill %>%
            select(`Team Position` = Team_Pos,
                   Club,
                   `Team Score` = score,
                   `Full Team` = Full_Team
                   ),
          rownames = FALSE, filter = "top")
```

#### Plot of Results

Clubs are ordered by their team position for veteran men (V40 and above). First 4 to score.

Total team score is shown in the top row, individual scores below with scorers highlighted.


```{r, echo=FALSE, warning=FALSE, fig.dim = c(8, 8)}
p$MenOneTreeHill
```

### Hainault

#### Table of Results


```{r, echo=FALSE}
datatable(vet_team_res$MenHainault %>%
            select(`Team Position` = Team_Pos,
                   Club,
                   `Team Score` = score,
                   `Full Team` = Full_Team
                   ),
          rownames = FALSE, filter = "top")
```

#### Plot of Results

Clubs are ordered by their team position for veteran men (V40 and above). First 4 to score.

Total team score is shown in the top row, individual scores below with scorers highlighted.


```{r, echo=FALSE, warning=FALSE, fig.dim = c(8, 8)}
p$MenHainault
```

```{r, include=FALSE, fig.dim = c(8, 8)}
for(race in names(vet_team_res)){
  
p1 <- 
  ggplot(vet_team_res[[race]], 
         aes(Club, score, text = paste0(Club, ", Team position: ", Team_Pos, ", Team score: ", score)))+
  geom_point(aes(colour = Club, fill = Club), shape=21, size=3)+
  scale_colour_manual(values = col_palette$club_colour)+
  scale_fill_manual(values = col_palette$club_fill)+
  scale_y_reverse()+
  facet_grid(.~Full_Team, scales="free_x", space="free")+
  labs(x = "", y = "Team score", title = paste0(gsub("Men", "", race), ", Vets"))+
  theme_classic()+
  theme(axis.text.x = element_blank(), 
        legend.position = "none",
        panel.background = element_rect(fill = 'slategrey'))

p2 <- 
  ggplot(res_vet[[race]], 
             aes(Club, Time, text=paste0(Name, ", Cat: ", Cat,
                             ", Time: ", Time,
                             ", Position: ", Pos, 
                             ", Vet position: ", Vet_Pos)))+
  geom_point(aes(colour = Club, fill = Club, alpha = Scorer_alpha), shape=21, size=2)+
  scale_colour_manual(values = col_palette$club_colour)+
  scale_fill_manual(values = col_palette$club_fill)+
  scale_y_reverse(labels = function(x) as_hms(x),
                  breaks=breaks)+
  facet_grid(.~Full_Team, scales="free_x", space="free")+
  labs(x = "", y="Time")+
  theme_classic()+
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position = "none",
        panel.background = element_rect(fill = 'slategrey'), 
        strip.text = element_blank())

# Convert ggplot objects to plotly objects using ggplotly()
fig1 <- ggplotly(p1, tooltip = "text")
fig2 <- ggplotly(p2, tooltip = "text")

p[[race]] <- subplot(fig1, fig2, nrows = 2, titleY = TRUE, heights = c(0.4, 0.6))
}

p$MenOneTreeHill
p$MenHainault
```

